\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
Discussion update

%% USP
Our approach is unique in that it captures fine scale population and fishery
dynamics and their interaction in a way not usually possible with real data and
thus not usually considered in fisheries simulations. While other simulation
frameworks seek to model individual vessel dynamics based on inferred dynamics
from VMS and logbook records \citep{Bastardie2010}, or as a system to identify
measures to meet particular management goals \citep{Bailey2018}, our framework
allows users to explore the assumptions in modelling observational data and
evaluate the underlying dynamics of such approaches at a fine spatial and
temporal scale.  This offers the advantage that larger scale fishery patterns
are emergent properties of the system rather and results can be compared to
those obtained under a statistical modelling framework. \\

%% Comparison to other models
Typically, simulation models which treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding how fleets which exploit multiple fish
populations realise catch distributions which may differ from the underlying
populations. As such, we favoured a minimum realistic model of the fish
populations after \cite{Plaganyi2014}, while incorporating fishing dynamics
which take account of different drivers in a mechanistic way, similarly to
other approaches \citep{Fulton2011} but at an individual vessel rather than
fleet level. We do not explicitly define fleets as rational profit maximisers
at the outset, but consider there are several stages to development of the
fishery; information gathering through search where the resource location is
not known,  followed by individual learnt behaviour of profitable locations.
This provides a realistic model of how fishing patterns are established and
maintained to exploit an uncertain resource \citep{Mangel1983, Bailey2018}.

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and that its important to consider the scale of process;
including population movement movement rates, habitat uniformity and fishing
targeting practices if potential biases in data are going to be addressed. Two
contrasting approaches in this respect were the spatial closures to protect cod
in the North Sea. In one example, large scale spatial closures were implemented
with little success due to effort displacement to previously unfished areas
\citep{Dinmore2003}, while in another small scale targeted spatiotemporal
closures were considered to have some effect in reducing cod mortality without
having to disrupt other fisheries significantly \citep{Needle2011}. These
emphasise the importance of considering the right scale and aggregation of data
when identifying area closures.
NOTE: CHECK THIS SECTION, IS A BIT "LOOSE".
\\

>>>>

%% USP
Our approach is unique in that it captures fine scale population and fishery
dynamics and their interaction in a way not usually possible with real data and
thus not usually considered in fisheries simulations. While other simulation
frameworks seek to model individual vessel dynamics based on inferred dynamics
from VMS and logbook records \citep{Bastardie2010}, or as a system to identify
measures to meet particular management goals \citep{Bailey2018}, our framework
allows users to explore the assumptions in modelling observational data and
evaluate the underlying dynamics of such approaches at a fine spatial and
temporal scale.  This offers the advantage that larger scale fishery patterns
are emergent properties of the system and results can be compared to those
obtained under a statistical modelling framework. \\

%% Comparison to other models
Typically, simulation models which treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
which may differ from the underlying populations. As such, we favoured a
minimum realistic model of the fish populations \citep{Plaganyi2014}, while
incorporating detailed fishing dynamics which take account of different drivers
in a mechanistic way. In this way we take account of heterogeneity in fleet
dynamics due to different preferences and drivers similarly to other approaches
\citep{Fulton2011}, but at an individual vessel rather than fleet level. We do
not explicitly define fleets as rational profit maximisers at the outset, but
consider there are several stages to development of the fishery; information
gathering through search where the resource location is not known,  followed by
individual learnt behaviour of profitable locations.  This provides a realistic
model of how fishing patterns are established and maintained to exploit an
uncertain resource through an explore-exploit strategy \citep{Mangel1983,
	Bailey2018}.

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and that its important to consider the scale of process;
including population movement movement rates, habitat uniformity and fishing
targeting practices if potential biases in data are to be understood and taken
into account. Two contrasting real world approaches in this respect were the
spatial closures to protect cod in the North Sea. In one example, large scale
spatial closures were implemented with little success due to effort
displacement to previously unfished areas \citep{Dinmore2003}, while in another
small scale targeted spatiotemporal closures were considered to have some
effect in reducing cod mortality without having to disrupt other fisheries
significantly \citep{Needle2011}. These examples emphasise the importance of
considering the right scale and aggregation of data when identifying area
closures and the need to consider changing dynamics in the fisheries in
response to such closures. \\
